Predicting Sequence Variability from Voronoi Tessellation of Proteins

### 2015-02-20 manuscript/voronoi/manuscript_voronoi.tex
minor changes

@@

>>>>

    \begin{figure}[tbh]
        \begin{center}
        \includegraphics[width=6.9in]{/voronoi_diagram.pdf}
        \end{center}
        \caption{Example 2-dimensional Voronoi diagram for bacteriophage T7 lysozyme (Protein Data Bank ID `1LBA'). The red dots represent the backbone $C_\alpha$ atoms projected on the X--Y plane, used as cell seeds in Voronoi tesellation.}
        \label{fig:voronoi}
    \end{figure}

@@

    \begin{figure}[tbh]
        \begin{center}
        \includegraphics[width=6.9in]{/best_structural_predictors_of_ER.pdf}
        \end{center}
        \caption{A comparison of the prediction power of four structural variables about site-specific evolutionary rates. Example 2-dimensional Voronoi diagram for bacteriophage T7 lysozyme (Protein Data Bank ID `1LBA'). The red dots represent the backbone $C_\alpha$ atoms projected on the X--Y plane, used as cell seeds in Voronoi tesellation.}
        \label{fig:best_predictor}
    \end{figure}
